
```{r}
#| label: setup-about
#| echo: false

# Import the data that will be used to create the tables.
# Import `combined_participant_data.rds`. This dataset is created in `link2care_public/data_survey_21_merge.Rmd`. Additionally, this code assumes that this file is being run from the SharePoint `General` folder.

# Use `source("R/import_data.R")` to import the data at the top of every .qmd file. That way, the information in Administrative Information table on the home page is correct for all tables.
# source("R/import_data.R")

# Update: I moved source("R/import_data.R") to an .Rprofile file. That way, the file only runs once, rather than at the beginning of each qmd file. If this approach continues to work, then I will erase the notes above. 
```

::: callout-warning
The information on this page is not likely to be useful to many users. Rather, this page is intended to assist with site maintenance.
:::

# Overview of the data

The data for these tables is currently housed at UTHealth-Houston on the [Link2Care SharePoint site](https://uthtmc.sharepoint.com/sites/Link2Careproject). Contact Brad Cannell at [Michael.B.Cannell\@uth.tmc.edu](mailto:Michael.B.Cannell@uth.tmc.edu) if you have questions about accessing the data.

The source data for all of the tables on this website is ``r df_nm``, which was created in the file `link2care_public/data_survey_21_merge.Rmd` and is stored on on the [Link2Care SharePoint site](https://uthtmc.sharepoint.com/sites/Link2Careproject) at ``r folder``.

After importing the data, we modify it in the following ways before creating the descriptive tables:

1. Keep rows for visit 1 and 2 only. The descriptive tables on this website currently contain _baseline_ statistics only. Most of the baseline data was collected at visit 1. However, there were a handful of survey measures that were collected for the first time at visit 2.

2. Keep rows for randomized participants only. We want the sample to include participants who were randomized only. We do _not_ include participants who attended visit 1, but were not randomized.

The modifications listed above are made in `import_data.R`.

The table below contains other administrative information about the data for tracking and maintenance purposes. 

# Administrative information about the data

```{r}
#| label: table-administrative
#| echo: false

# Turn numeric values into character strings for the table 
today <- as.character(Sys.Date())
rows <- as.character(df_dim[1])
columns <- as.character(df_dim[2])
n_overall <- as.character(n_participants) 
n_ucm <- as.character(n_per_group["UCM"])
n_ucmsp <- as.character(n_per_group["UCM+SP"])
n_l2c <- as.character(n_per_group["L2C"])

admin_info <- tibble::tribble(
  ~Attribute,                  ~Value,    ~Description,
  "Last updated:",             today,     "The date the tables on this website were last updated.",
  "Source data:",              df_nm,     "The name of the dataset used to create the tables on this website.",
  "Source data path:",         folder,    "The path to the source data.",
  "Source data size:",         df_size,   "The size of the modified data used to create the tables on this website.",
  "Source data row count:",    rows,      "The number of rows currently contained in the data used to create the tables on this website.",
  "Source data column count:", columns,   "The number of columns/variables currently contained in the data used to create the tables on this website.",
  "N participants:",           n_overall, "The number of unique participants in the data used to create the tables on this website.",
  "N UCM participants:",       n_ucm,     "The number of unique participants in the data who were in the usual care management arm of the Link2Care study.",
  "N UCM+SP participants:",    n_ucmsp,   "The number of unique participants in the data who were in the usual care management plus smart phone arm of the Link2Care study.",
  "N L2C participants:",       n_l2c,     "The number of unique participants in the data who were in the Link2Care arm of the Link2Care study."
)

knitr::kable(admin_info, align = c("l", "c", "c"))
```

# Codebook

The full codebook for the source data is available at: <https://github.com/brad-cannell/link2care_public/blob/master/codebooks/Combined%20Participant%20Survey%20Data%20Codebook.pdf>
