---
title: "Discrepancies Decision Data Checks"
---

This document was made in anticipation of a research team meeting to discuss differences within the data that may impact analytical decisions.

# Libraries

```{r, warning = FALSE, message = FALSE}
library(here)
library(tidyverse)
library(readxl, warn.conflicts = FALSE)
library(haven)
```

# Data

The combined data set is stored as `baseline_data`, and imported using the master table script.

```{r}
source(here("R/import_data.R"))

# Print a message for when this file is being sourced
cat(
  paste0(Sys.Date(), ":"),
  "Combined Participant Baseline Data imported with", 
  nrow(baseline_data), "rows and", 
  ncol(baseline_data), "columns.\n"
)

# Check the most recent file modification dates and print for user when this
# file is being sourced.

cat(
      "Combined Participant Data last modified on OneDrive", 
      as.character(file.info(path)$mtime), "\n"
    )

# 2023-11-03: Combined Participant Baseline Data imported with 442 rows and 
# 1037 columns.
# Combined Participant Data last modified on OneDrive 2023-10-27 16:06:04 
```

The remaining data was stored in the Link2Care public data folders.

```{r}
base_path <- paste0(
    substring(
        here::here(), 
        1, 
        nchar(here::here())-nchar('link2care_master_table')
    ),
    'link2care_public/data/'
    )
```


The Bridge Session rows identified as potentially containing typos in the date field were imported as `bridge_subset`.

```{r}
bridge_path <- paste0(
    base_path,
    'bridge_session_data/bridge_0_questionable_cols.rds'
  )

bridge_subset <- readRDS(bridge_path)

# Print a message for when this file is being sourced
cat(
  paste0(Sys.Date(), ":"),
  "Isolated Bridge Data imported with", nrow(bridge_subset), 
  "rows and", ncol(bridge_subset), "columns.\n"
)

# Check the most recent file modification dates and print for user when this
# file is being sourced.

cat(
      "Isolated Bridge Data last modified on OneDrive", 
      as.character(file.info(bridge_path)$mtime), "\n"
    )

# 2023-11-03: Isolated Bridge Data imported with 107 rows and 10 columns.
# Isolated Bridge Data last modified on OneDrive 2023-10-23 09:51:36 
```

The Master Log was inported as `master_log`.

```{r}
master_log_path  <- paste0(
  base_path,
  'master_log/master_log.xlsx'
  )

master_log <- read_excel(
  master_log_path, 
  sheet = "Screened In",
  col_names = c(
    "id", "baseline_dt",
    "v2_dt", 
    "v3_dt", 
    "v4_dt", 
    "v5_dt",
    "group", "v2_status", "dropped_status", 
    "name_first", "name_middle", "name_last",
    "gender", "race", "hispanic_latino", "dob", "age", 
    "care_manager"
    ),
  col_types = c(
    "text", "skip", "date", rep("skip", 2),
    "date", rep("skip", 4), 
    "date", rep("skip", 4),
    "date", rep("skip", 4),
    "date", rep("skip", 2),
    rep("text", 3),
    rep("text", 3),
    rep("text", 3), "date", "text",
    rep("skip", 5), "text",
    rep("skip", 15)
    ),
  skip = 1
) |> 
  # Coerce group to numeric so that it can be combined with the QDS data.
  mutate(
    group = case_when(
      group == "UCM"    ~ 1,
      group == "UCM+SP" ~ 2,
      group == "L2C"    ~ 3
    )
  ) |>
  # Coerce age to a numeric
  mutate(age = as.numeric(age)) |>
  # Remove empty rows
  filter(!is.na(id))

# Print a message for when this file is being sourced
cat(
  paste0(Sys.Date(), ":"),
  "Master log imported with", nrow(master_log), "rows and", ncol(master_log),
  "columns.\n"
)

# Check the most recent file modification dates and print for user when this
# file is being sourced.

cat(
      "Master log last modified on OneDrive", 
      as.character(file.info(master_log_path)$mtime), "\n"
    )

# 2023-11-03: Master log imported with 442 rows and 18 columns.
# Master log last modified on OneDrive 2023-09-28 11:52:59
```

The full Bridge Session data was inported as `bridge_full`.

```{r}
bridge_path <- paste0(
  base_path,
  "bridge_session_data/bridge_session_minutes.xlsx"
  )

bridge_full <- read_excel(
  bridge_path,
  sheet = "Sheet1",
  col_names = c(
    "subject", "bridge_baseline_date", "bridge_v2_rand_date", 
    "bridge_v5_sched_final_visit_date", "bridge_date_session", "bridge_type", 
    "bridge_duration", "bridge_flag_ns_v2", "bridge_flag_dropped", 
    "bridge_notes"
  ),
  col_types = c(
    "numeric", rep("date", 3), "text", rep("numeric", 4), "text"
  ),
  na = c("", ".", "None"),
  skip = 10
)

# Print a message for when this file is being sourced
cat(
  paste0(Sys.Date(), ":"),
  "Bridge Data imported with", nrow(bridge_full), "rows and", 
  ncol(bridge_full),"columns.\n"
)

# Check the most recent file modification dates and print for user when this
# file is being sourced.

cat(
      "Bridge Data last modified on OneDrive", 
      as.character(file.info(bridge_path)$mtime), "\n"
    )

# 2023-11-03: Bridge Data imported with 4377 rows and 10 columns.
# Bridge Data last modified on OneDrive 2023-08-25 10:43:48 
```

# Modifications to Facilitate Isolation with R

## Bridge Data Processing

We repeated some standardization cleaning performed in data_survey_01_preprocess.qmd, which served to clean the Bridge Data in a way that R could utilize the information.

```{r}
# Remove non-date entries from date column, and convert to date

bridge_full <- bridge_full |>
  mutate(
    bridge_date_session = if_else(
      str_detect(bridge_date_session, "[A-Z]|[a-z]"), 
      NA_character_, bridge_date_session
    ),
    bridge_date_session = as.numeric(bridge_date_session),
    bridge_date_session = as.Date(bridge_date_session, origin = "1899-12-30")
  )

# Remove content of 'notes' rows

bridge_full[1, "bridge_notes"] <- NA_character_
bridge_full[2, "bridge_notes"] <- NA_character_

# Remove rows that only contained missing values

bridge_full <- bridge_full |>
  # Create missing data dummy variables
  mutate(
    across(
      everything(),
      is.na,
      .names = "{col}_miss"
    )
  ) |> 
  # Sum missing data dummy variables
  rowwise() |> 
  mutate(
    n_missing = sum(c_across(ends_with("_miss")))
  ) |> 
  ungroup() |> 
  # Drop missing data dummy variables
  select(-ends_with("_miss")) |> 
  # Drop rows that are missing in every column
  filter(!n_missing == ncol(bridge_full)) |>
  # Drop the count of missing variables
  select(-n_missing)

# Carry forward variables that were only listed on the first set of rows
# for a subject

bridge_full <- bridge_full |>
  # Carry forward id
  fill(subject) |> 
  group_by(subject) |> 
  # Carry forward other variables grouped by id
  fill(
    bridge_baseline_date, bridge_v2_rand_date, bridge_v5_sched_final_visit_date
  ) |> 
  ungroup()

# Convert session-type ('bridge_type') into a factor

bridge_full <- bridge_full |>
    mutate(
    # Change NA to None for type
    bridge_type = if_else(is.na(bridge_type), 4, bridge_type),
    # Create factor version
    bridge_type_f = factor(
      bridge_type,
      1:4,
      c("case_management", "crisis_management", "other", "none")
    )
  )

# Warning: There was 1 warning in `mutate()`.
# ℹ In argument: `bridge_date_session = as.numeric(bridge_date_session)`.
# Caused by warning:
# ! NAs introduced by coercion
```

## Flagging Discrepancies between Master Log and Subjective Versions of Demographics

We flagged any row that had a discrepancy between the subject-given value column, and the master-log recorded value column, for our key demographic variables: age, race, hispanic ethnicity, and sex/gender.

```{r}
baseline_data <- baseline_data |>
  dplyr::mutate(
      age_diff = ifelse(sq_04_subj_age != sq_04_subj_age_ml, TRUE, FALSE),
      race_diff = ifelse(sq_03_subj_race != sq_03_subj_race_ml, TRUE, FALSE),
      hispanic_diff = ifelse(
          sq_02_subj_hispanic != sq_02_subj_hispanic_ml, 
          TRUE, 
          FALSE
        ),
      gender_diff = ifelse(sq_01_subj_gender != sq_01_subj_gender_ml, TRUE, FALSE)
    )
```

# Demographic Differences (Master Log vs Subject Responses)

## Sex/Gender

There were no subjects with a discrepancy in Sex/Gender values

```{r}
sum(baseline_data$gender_diff)
```

## Race

There were 12 subjects with a discrepancy in Race values: 

2182, 2210, 2215, 2260, 2266, 2323, 2333, 2344, 2358, 2380, 2400, 2409

```{r}
race_ids <- pull(
  baseline_data |>
    filter(race_diff) |>
    select(id) |>
    distinct()
  )

length(race_ids)
```

In inspecting these subjects, we can see that only race varied for these subjects (hispanic ethnicity was consistent). 

```{r}
baseline_data |>
  filter(race_diff) |>
  select(
    id, sq_03_subj_race, sq_03_subj_race_ml, 
    sq_02_subj_hispanic, sq_02_subj_hispanic_ml
    )
```


## Hispanic Ethnicity

There were 4 subjects with a discrepancy in Hispanic Ethnicity values: 

2148, 2295, 2381, 2420

```{r}
ethn_ids <- pull(
  baseline_data |>
    filter(hispanic_diff) |>
    select(id) |>
    distinct()
  )

length(ethn_ids)
```

In viewing these subjects, we note the subjects identified themselves as Hispanic, but they were not identified as Hispanic in the Master Log. Race was consistent for all subjects.

```{r}
baseline_data |>
  filter(hispanic_diff) |>
  select(
    id, sq_03_subj_race, sq_03_subj_race_ml, 
    sq_02_subj_hispanic, sq_02_subj_hispanic_ml
    )
```

## Age

There were 33 subjects with a discrepancy in Age values between Subjective responses and the Master Log: 

2006, 2023, 2080, 2087, 2099, 2120, 2126, 2130, 2144, 2145, 2161, 2176, 2180, 2210, 2229, 2240, 2253, 2265, 2266, 2269, 2290, 2304, 2322, 2324, 2326, 2333, 2339, 2349, 2357, 2358, 2365, 2434, 2437

```{r}
age_ids <- pull(
  baseline_data |>
    filter(age_diff) |>
    select(id) |>
    distinct()
  )

length(age_ids)
```

In viewing these subjects, we note that the subject-provided ages appear more consistent with age calculated from the subject's date of birth (from the master log) against the baseline collection date.

```{r}
baseline_data |>
  filter(age_diff) |>
  mutate(
    diff_subj_ml = sq_04_subj_age - sq_04_subj_age_ml,
    diff_subj_calc = sq_04_subj_age - sq_04_subj_age_calc,
    diff_ml_calc = sq_04_subj_age_ml - sq_04_subj_age_calc
  )|>
  select(
    id, sq_04_subj_age, sq_04_subj_age_ml, sq_04_subj_age_calc,
    diff_subj_ml, diff_subj_calc, diff_ml_calc
  )
```

# Bridge Session Differences

There were 107 individual dates, across 31 subjects, in the Bridge Session Data that appeared to contain typographic errors, placing the date outside of the range of data collection for a subject.

```{r}
bridge_subj_list <- unique(bridge_subset$subject)
nrow(bridge_subset)
length(bridge_subj_list)
```

We can examine each subject individually in the full bridge data. The visits identified in the subset were flagged, and the recorded date of visit 5 for the subject was also included. 

```{r}
target_subject <- bridge_subj_list[1]

subject_dates <- pull(
  bridge_subset |>
    filter(subject == target_subject) |>
    select(bridge_date_session)
)

bridge_full |>
  filter(subject == target_subject) |>
  select(
    subject, bridge_date_session, bridge_baseline_date, 
    bridge_v5_sched_final_visit_date, bridge_flag_dropped
    ) |>
  mutate(
    flag_visit = (bridge_date_session %in% subject_dates),
    ml_v5_dt = master_log[master_log$id == target_subject,]$v5_dt
  ) |>
  relocate(subject, flag_visit, ml_v5_dt)
```

